Reply to Reviewer #1

### 2022-03-15 Writing/CEA_2nd_round/replies_rev_1.rmd
minor edits
CEA 3rd round

Thank you so much for your comments. By addressing them, we believe the manuscript is improved significantly. Below you will find your comments in bold and our replies in a regular font.

@@

First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$. In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1.1, Figure C.1.1).

@@

<span style="color:blue">  
We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://data.mendeley.com/datasets/y7cdhzww6w/draft?a=2e33b309-ca5c-49bc-95ce-9b3920d5544a) to increase the accessibility. The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data". The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study. Please read README.md for the steps to reproduce. In addition, we also created a public github repository named CF_for_VRA ([here](https://github.com/tmieno2/CF_for_VRA)).
</span>

@@

<span style="color:blue">  
We modified the length units (line 162) 
</span>

>>>>

Thank you so much for your comments. By addressing them, we believe the manuscript has improved significantly. Below you will find your comments in bold and our replies in regular font.

@@

First, in the new manuscript we consolidated the original manuscript's 3.1.2 and 3.1.3 into a single subsubsection called "Cell-specific Yield Functions and True Economically Optimal N Rates." In doing so, we moved to the supplementary appendix (Appendix B) the detailed explanation of the conceptual framework behind the yield response functions based on cell-level characteristics, $c_i$. In addition, we moved to Appendix C our detailed discussion of parameters and error term generation, which included a number of tables and figures (Table C.1, Figure C.1).

@@

<span style="color:blue">  
We have followed the Editor's suggestion by sharing the simulation codes and the data on Mendeley Data (https://doi.org/10.17632/y7cdhzww6w.1) to increase the accessibility. The name of the data set is "Codes and Data Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation", and two folders are included in this data set: "Codes" and  "Data". The "Code" folder contains all the simulation codes, and the "Data" folder contains a boundary polygon data of a field which is necessary to create field data for this study. Please read README.md for the steps to reproduce. In addition, we also created a public github repository named VRA_with_CF (https://github.com/Shunkei3/VRA_with_CF.git).
</span>

@@

<span style="color:blue">  
We modified the length units (line 163) 
</span>
